Poster Data Analysis

### 2018-09-06 notebooks/poster_analysis.Rmd
fixed imported files to correct ID settings

# Import data
This chunk imports data from MLST and ARIBA AMR gene detection results. Isolate data is also imported.
```{r}
# Isolate data, including DNA extraction results, species,
# method of isolation, and sequencing methodology
isolate_data <- read.table("../data/total_data.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F)

# ARIBA MLST results for each isolate
mlst_results <- read.table("../data/mlst/mlst_results.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F)

@@

@@

# Figures
## Percent presence of acquired genes in total
```{r}
resfinder_results %>%
  gather(gene, result, -c(saksnr, type)) %>%
  group_by(gene, result) %>%
  count() %>%
  ungroup() %>%
  mutate(result = if_else(result == 1, "Present", "Absent")) %>%
  spread(result, n, fill = 0) %>%
  rowwise() %>%
  mutate(Total = Present + Absent,
         Percent = round(Present/Total*100, 1),
         lwr = round(get_binCI(Present, Total)[1], 1),
         upr = round(get_binCI(Present, Total)[2], 1)) %>%
  ggplot(aes(gene, Percent))+
  geom_col(color = "black")+
  geom_errorbar(aes(ymin = lwr, ymax = upr),
                width = 0.6)+
  labs(y = "Percent (%) of isolates")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90, size = 8, hjust = 1, vjust = 0.4),
        axis.title.x = element_blank())
```

## Percent presence of mutations in intrinsic genes in total
```{r}
megares_results %>%
  gather(gene, result, -c(saksnr, type)) %>%
  group_by(gene, result) %>%
  count() %>%
  ungroup() %>%
  mutate(compl = complete.cases(.),
         result = if_else(result == 1, "Present", "Absent")) %>%
  filter(compl == TRUE) %>%
  select(-compl) %>%
  spread(result, n, fill = 0) %>%
  rowwise() %>%
  mutate(Total = Present + Absent,
         Percent = round(Present/Total*100, 1),
         lwr = round(get_binCI(Present, Total)[1], 1),
         upr = round(get_binCI(Present, Total)[2], 1)) %>%
  ggplot(aes(gene, Percent))+
  geom_col(color = "black")+
  geom_errorbar(aes(ymin = lwr, ymax = upr),
                width = 0.6)+
  labs(y = "Percent (%) of isolates")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90, size = 8, hjust = 1, vjust = 0.4),
        axis.title.x = element_blank())
```

## Acquired genes per animal species
```{r}

gene_names <- names(resfinder_results)

resfinder_results %>%
  left_join(isolate_data, by = "saksnr") %>%
  left_join(isolate_data, by = c("saksnr" = "plate_id")) %>%
  mutate(species.y = if_else(is.na(species.y) == TRUE, species.x, species.y),
         saksnr.y = if_else(is.na(saksnr.y) == TRUE, saksnr, saksnr.y),
         method.y = if_else(is.na(method.y) == TRUE, method.x, method.y),
         id = paste(saksnr.y, method.y, sep = "-"),
         dupl = duplicated(id)) %>%
  filter(dupl == FALSE) %>%
  gather(key, value, gene_names) %>%
  group_by(key, value, species.y) %>%
  count() %>%
  ungroup() %>%
  mutate(value = if_else(value == 1, "Present", "Absent")) %>%
  spread(value, n, fill = 0) %>%
  rowwise() %>%
  mutate(Total = Present + Absent,
         Percent = round(Present/Total*100, 1),
         lwr = round(get_binCI(Present, Total)[1], 1),
         upr = round(get_binCI(Present, Total)[2], 1)) %>%
  ggplot(aes(key, Percent, fill = species.y))+
  geom_col(color = "black",
           position = position_dodge(1))+
  geom_errorbar(aes(ymin = lwr, ymax = upr),
                width = 0.6,
                position = position_dodge(1))+
  labs(y = "Percent (%) of isolates")+
  guides(fill = FALSE)+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90, size = 8, hjust = 1, vjust = 0.4),
        axis.title.x = element_blank())+
  facet_wrap(~species.y)
```

# Mutations in intrinsic genes per animal species
```{r}
mut_names <- names(megares_results)

megares_results %>%
  left_join(isolate_data, by = "saksnr") %>%
  left_join(isolate_data, by = c("saksnr" = "plate_id")) %>%
  mutate(species.y = if_else(is.na(species.y) == TRUE, species.x, species.y),
         saksnr.y = if_else(is.na(saksnr.y) == TRUE, saksnr, saksnr.y),
         method.y = if_else(is.na(method.y) == TRUE, method.x, method.y),
         id = paste(saksnr.y, method.y, sep = "-"),
         dupl = duplicated(id)) %>%
  filter(dupl == FALSE) %>%
  gather(key, value, mut_names) %>%
  group_by(key, value, species.y) %>%
  count() %>%
  ungroup() %>%
  mutate(compl = complete.cases(.),
         value = if_else(value == 1, "Mutant", "Wild Type")) %>%
  filter(compl == TRUE) %>%
  spread(value, n, fill = 0) %>%
  rowwise() %>%
  mutate(Total = Mutant + `Wild Type`,
         Percent = round(Mutant/Total*100, 1),
         lwr = round(get_binCI(Mutant, Total)[1], 1),
         upr = round(get_binCI(Mutant, Total)[2], 1)) %>%
  ggplot(aes(key, Percent, fill = species.y))+
  geom_col(color = "black",
           position = position_dodge(1))+
  geom_errorbar(aes(ymin = lwr, ymax = upr),
                width = 0.6,
                position = position_dodge(1))+
  labs(y = "Percent (%) of isolates")+
  guides(fill = FALSE)+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90, size = 8, hjust = 1, vjust = 0.4),
        axis.title.x = element_blank())+
  facet_wrap(~species.y)
```

>>>>

# Import data
This chunk imports data from MLST and ARIBA AMR gene detection results. Isolate data is also imported.
```{r}
# Isolate data, including DNA extraction results, species,
# method of isolation, and sequencing methodology
isolate_data <- read.table("../data/isolate_data.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F)

# Total MIC profile for all isolates in this study
mic_data <- read.table("../data/mic_data.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F)

# ARIBA MLST results for each isolate
mlst_results <- read.table("../data/mlst_results.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F)

@@

total_data <- isolate_data %>%
  left_join(mic_data) %>%
  left_join(mlst_results) %>%
  rename("m_gyrB" = gyrB) %>%
  left_join(resfinder_results) %>%
  select(-type) %>%
  left_join(megares_results) %>%
  select(-type)
```

# Figures
## Percent presence of acquired genes in total
```{r}
resfinder_results %>%
  gather(gene, result, -c(id, type)) %>%
  group_by(gene, result) %>%
  count() %>%
  ungroup() %>%
  mutate(result = if_else(result == 1, "Present", "Absent")) %>%
  spread(result, n, fill = 0) %>%
  rowwise() %>%
  mutate(Total = Present + Absent,
         Percent = round(Present/Total*100, 1),
         lwr = round(get_binCI(Present, Total)[1], 1),
         upr = round(get_binCI(Present, Total)[2], 1)) %>%
  ggplot(aes(gene, Percent))+
  geom_col(color = "black")+
  geom_errorbar(aes(ymin = lwr, ymax = upr),
                width = 0.6)+
  labs(y = "Percent (%) of isolates")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90, size = 8, hjust = 1, vjust = 0.4),
        axis.title.x = element_blank())
```

## Percent presence of mutations in intrinsic genes in total
```{r}
megares_results %>%
  gather(gene, result, -c(id, type)) %>%
  group_by(gene, result) %>%
  count() %>%
  ungroup() %>%
  mutate(compl = complete.cases(.),
         result = if_else(result == 1, "Present", "Absent")) %>%
  filter(compl == TRUE) %>%
  select(-compl) %>%
  spread(result, n, fill = 0) %>%
  rowwise() %>%
  mutate(Total = Present + Absent,
         Percent = round(Present/Total*100, 1),
         lwr = round(get_binCI(Present, Total)[1], 1),
         upr = round(get_binCI(Present, Total)[2], 1)) %>%
  ggplot(aes(gene, Percent))+
  geom_col(color = "black")+
  geom_errorbar(aes(ymin = lwr, ymax = upr),
                width = 0.6)+
  labs(y = "Percent (%) of isolates")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90, size = 8, hjust = 1, vjust = 0.4),
        axis.title.x = element_blank())
```

## Acquired genes per animal species
```{r}
gene_names <- names(resfinder_results)

resfinder_results %>%
  left_join(isolate_data, by = "id") %>%
  gather(key, value, gene_names) %>%
  group_by(key, value, species) %>%
  count() %>%
  ungroup() %>%
  mutate(value = if_else(value == 1, "Present", "Absent")) %>%
  spread(value, n, fill = 0) %>%
  rowwise() %>%
  mutate(Total = Present + Absent,
         Percent = round(Present/Total*100, 1),
         lwr = round(get_binCI(Present, Total)[1], 1),
         upr = round(get_binCI(Present, Total)[2], 1)) %>%
  ggplot(aes(key, Percent, fill = species))+
  geom_col(color = "black",
           position = position_dodge(1))+
  geom_errorbar(aes(ymin = lwr, ymax = upr),
                width = 0.6,
                position = position_dodge(1))+
  labs(y = "Percent (%) of isolates")+
  guides(fill = FALSE)+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90, size = 8, hjust = 1, vjust = 0.4),
        axis.title.x = element_blank())+
  facet_wrap(~species)
```

## Mutations in intrinsic genes per animal species
```{r}
mut_names <- names(megares_results)

megares_results %>%
  left_join(isolate_data, by = "id") %>%
  gather(key, value, mut_names) %>%
  group_by(key, value, species) %>%
  count() %>%
  ungroup() %>%
  mutate(value = if_else(value == 1, "Mutant", "Wild Type"),
         compl = complete.cases(.)) %>%
  filter(compl == TRUE) %>%
  spread(value, n, fill = 0) %>%
  rowwise() %>%
  mutate(Total = Mutant + `Wild Type`,
         Percent = round(Mutant/Total*100, 1),
         lwr = round(get_binCI(Mutant, Total)[1], 1),
         upr = round(get_binCI(Mutant, Total)[2], 1)) %>%
  ggplot(aes(key, Percent, fill = species))+
  geom_col(color = "black",
           position = position_dodge(1))+
  geom_errorbar(aes(ymin = lwr, ymax = upr),
                width = 0.6,
                position = position_dodge(1))+
  labs(y = "Percent (%) of isolates")+
  guides(fill = FALSE)+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90, size = 8, hjust = 1, vjust = 0.4),
        axis.title.x = element_blank())+
  facet_wrap(~species)
```

## MIC plots
```{r}

@@
